---
title: "Untitled"
author: "Michael Mullarkey"
date: "9/28/2021"
output: html_document
---

```{r setup, include=FALSE, cache = FALSE}
require("knitr")
knitr::opts_chunk$set(echo = TRUE, tidy = TRUE, warning = FALSE, message = FALSE, include = FALSE)
```

```{r loading packages}

if(!require(tidymodels)){install.packages('tidymodels')}
library(tidymodels)
if(!require(tidyverse)){install.packages('tidyverse')}
library(tidyverse)
if(!require(skimr)){install.packages('skimr')}
library(skimr)
if(!require(furrr)){install.packages('furrr')}
library(furrr)
if(!require(scales)){install.packages('scales')}
library(scales)
if(!require(tictoc)){install.packages('tictoc')}
library(tictoc)
if(!require(heatmaply)){install.packages('heatmaply')}
library(heatmaply)
if(!require(doMC)){install.packages('doMC')}
library(doMC)
if(!require(glue)){install.packages('glue')}
library(glue)
if(!require(janitor)){install.packages('janitor')}
library(janitor)
if(!require(future)){install.packages('future')}
library(future)
if(!require(remotes)){install.packages('remotes')}
library(remotes)
if(!require(psych)){install.packages('psych')}
library(psych)
if(!require(imputeTS)){install.packages('imputeTS')}
library(imputeTS)
if(!require(timetk)){install.packages('timetk')}
library(timetk)
if(!require(tsibble)){install.packages('tsibble')}
library(tsibble)
if(!require(feasts)){install.packages('feasts')}
library(feasts)
if(!require(dtw)){install.packages('dtw')}
library(dtw)
if(!require(parallelDist)){install.packages('parallelDist')}
library(parallelDist)
if(!require(pheatmap)){install.packages('pheatmap')}
library(pheatmap)
if(!require(diffdf)){install.packages('diffdf')}
library(diffdf)
if(!require(tableone)){install.packages('tableone')}
library(tableone)
if(!require(tableone)){install.packages('tableone')}
library(tableone)
if(!require(corrr)){install.packages('corrr')}
library(corrr)
if(!require(Amelia)){install.packages('Amelia')}
library(Amelia)
if(!require(MOTE)){install.packages('MOTE')}
library(MOTE)
if(!require(fuzzyjoin)){install.packages('fuzzyjoin')}
library(fuzzyjoin)
if(!require(car)){install.packages('car')}
library(car)
if(!require(lsmeans)){install.packages('lsmeans')}
library(lsmeans)
if(!require(fastDummies)){install.packages('fastDummies')}
library(fastDummies)
if(!require(lubridate)){install.packages('lubridate')}
library(lubridate)
if(!require(modeltime)){install.packages('modeltime')}
library(modeltime)
if(!require(tibbletime)){install.packages('tibbletime')}
library(tibbletime)


```

```{r parallelize}
## Let's set our number of cores for this document (May differ across computers)

registerDoMC(cores = 7)

## Benign change to see if Git is working

```

General plan here:

LifePak data

1. Get a sense of the original data format
2. Do initial cleaning (ordering notifications within participant, creating time of response)

```{r reading in all likepak files}

# Creating a file list of all csvs in working directory 

files <- list.files(pattern = "*.csv")

# Creating a file list of only Qualtrics files

lifepak_files <- files[c(1:5)]

# Importing in data without variable names (Have to skip the first few rows because of Qualtrics' format)

all_likepak <- lifepak_files %>% 
  map(~read_csv(.x, skip = 1, col_names = FALSE))

# Creating variable names from those same files

all_lifepak_names <- lifepak_files %>%
  map(read_csv) %>% 
  map(~slice_head(.x)) %>% 
  map(~names(.x)) %>% 
  map(~make_clean_names(.x))

# Adding the names to the imported data

named_lifepak <- map2(all_likepak, all_lifepak_names, ~{
  
  names(.x) <- .y  
  .x
  
})

```

```{r doing visual inspection of lifepak data}

map(1:5, ~{
  enframe(named_lifepak[.x]) %>% 
  dplyr::select(value) %>% 
  unnest(value) %>% 
  skim()
})

```

```{r identifying where the variable names do not match across dataframes}

# All variables AREN"T in the same order across the dataframes AND for some reason the names were also changed.

enframe(named_lifepak[1]) %>% 
  dplyr::select(value) %>% 
  unnest(value) %>% 
  names() %>% 
  enframe() %>% 
  separate(value, into = c("first", "rest"), "_") %>% 
  select(first) %>% 
  deframe()

var_name_first <- map(1:5, ~(
  enframe(named_lifepak[.x]) %>% 
  dplyr::select(value) %>% 
  unnest(value) %>% 
  names() %>% 
  enframe() %>% 
  separate(value, into = c("first", "rest"), "_") %>% 
  select(first) %>% 
  deframe()
  ))

```

```{r maybe time to rename the instruct and intro variables that mess up the alphabetical order fix for the columns being jumbled}

enframe(named_lifepak[1]) %>% 
  dplyr::select(value) %>% 
  unnest(value) %>% 
  dplyr::select(contains("instruct"))

enframe(named_lifepak[2]) %>% 
  dplyr::select(value) %>% 
  unnest(value) %>% 
  dplyr::select(contains("intro"))

```


```{r try putting names in alphabetical order since many start with the same prefixes}

enframe(named_lifepak[1]) %>% 
  dplyr::select(value) %>% 
  unnest(value) %>% 
  select(-contains("instruct"),-contains("intro")) %>% 
  select(order(colnames(.)))

alpha_order <- map(1:5, ~{
  enframe(named_lifepak[.x]) %>% 
  dplyr::select(value) %>% 
  unnest(value) %>% 
  select(-contains("instruct"),-contains("intro")) %>% 
  select(order(colnames(.)))
})

## Now are they in the same order?

alpha_name_first <- map(1:5, ~(
  enframe(alpha_order[.x]) %>% 
  dplyr::select(value) %>% 
  unnest(value) %>% 
  names() %>% 
  enframe() %>% 
  separate(value, into = c("first", "rest"), "_") %>% 
  select(first) %>% 
  deframe()
  )) %>% 
  print()

```

```{r seeing if these variables are actually ordered the same across data frames}

first <- 1:5
second <- 1:5

# Solved the duplicates problem using this solution https://stackoverflow.com/questions/29170099/remove-duplicate-column-pairs-sort-rows-based-on-2-columns

comp_df <- expand_grid(first, second) %>% 
  filter(first != second) %>% 
  rowwise() %>%
  mutate(key = paste(sort(c(first, second)), collapse="")) %>%
  distinct(key, .keep_all = TRUE) %>%
  select(-key) %>% 
  print()

discrep_names <- map2(comp_df$first, comp_df$second, ~{
  alpha_name_first[[.x]] == alpha_name_first[[.y]]
}) %>% 
  print()

# A vector of which values are true, showing matches across dataframes. Bottom line, we have several different patterns of missingness here so lots of regular methods won't work
# map(1:10, ~{
#   which(discrep_names[[.x]])
# })

```

```{r verifying number of participants}

map(1:5, ~(
  enframe(alpha_order[.x]) %>% 
  dplyr::select(value) %>% 
  unnest(value) %>% 
  group_by(participant_id) %>% 
  tally()
)) %>% 
  bind_rows()

# Verifying one participant who had 3 different IDs due to download errors (See README file on Lab Server)

map(1:5, ~(
  enframe(alpha_order[.x]) %>% 
  dplyr::select(value) %>% 
  unnest(value) %>% 
  group_by(participant_id) %>% 
  tally()
)) %>% 
  bind_rows() %>% 
  filter(participant_id == "21441-034516")

map(1:5, ~(
  enframe(alpha_order[.x]) %>% 
  dplyr::select(value) %>% 
  unnest(value) %>% 
  group_by(participant_id) %>% 
  tally()
)) %>% 
  bind_rows() %>% 
  filter(participant_id == "21476-878753")

```
```{r creating dataframe with all participants and columns}

all_df <- map(c(1:5), ~(
  enframe(alpha_order[.x]) %>% 
  dplyr::select(value) %>% 
  unnest(value) %>% 
  select(-contains("gps")) %>% 
  mutate(across(contains("responded"), as.character),
         # across(ends_with("day"), as.numeric),
         # across(ends_with("night"), as.numeric))
  )
)
) %>% 
  bind_rows() %>% 
  select(!where(is.logical)) %>% # Dropping logical columns since none of them are valid (All the 347 variables that weren't ever relevant)
  print()


```
```{r reordering notifications in chronological order and other initial cleaning}

## This is going through this for one test dataframe, we'll want a function that will let us map through all the dataframes in our list

temp <- all_df %>% 
  group_by(participant_id) %>% 
  mutate(response_time = case_when(
    responded != "User didn't respond to this notification" ~ notification_time + session_instance_response_lapse + session_length,
    TRUE ~ NA_POSIXct_
      )
    ) %>% 
  arrange(notification_time, .by_group = TRUE) %>% 
  mutate(response_no = row_number(),
         time_diff = as.numeric(response_time - lag(notification_time)), # This is in hours but I just need to make sure there aren't any negatives
         ) %>% 
  ungroup() %>% 
  relocate(participant_id, response_no, notification_no, notification_time, response_time, time_diff) %>% 
  print()

## Want to check that response time for first notification isn't later than the next notification (This is hack-y right now, but a positive number indicates no out of order responses)

temp %>% 
  filter(!is.na(time_diff)) %>% 
  count(time_diff) %>% 
  arrange(time_diff) %>% 
  slice_head()

```

```{r figuring out which variables need to be combined}

skim(temp)

```

```{r trying to pivot these columns longer}

# Let's see if we can do it for one kind of variable first

# This might be incomplete since it doesn't know what number this should go up to (106 or 107) but at least gets us most of the way there
# Maybe we can use the DataEditR package to add rows to groups if needed like I saw Asmae reference?

temp %>% 
  select(participant_id, response_no, contains("sad")) %>%
  pivot_longer(cols = contains("sad"),
               names_to = c(".value", "timing", "type"),
               names_sep = "_") %>% 
  mutate(type = case_when(
    is.na(type) ~ "orig",
    TRUE ~ type
  )) %>% 
  filter(!is.na(sad)) %>% 
  complete(participant_id, nesting(response_no)) # Try to figure out how to do this minimally so we can left_join a bunch of versions of this together programatically after mapping through a bunch of different variables. This version will work for the 2 underscore variables, will need to have another for the 3 underscore variables
  

## Write function for two underscore variables

tidy_two_underscore <- function(.data, contains_text){
  
    .data %>% 
      select(participant_id, response_no, contains(contains_text)) %>%
      pivot_longer(cols = contains(contains_text),
               names_to = c(".value", "timing", "type"),
               names_sep = "_") %>% 
      mutate(type = case_when(
            is.na(type) ~ "orig",
            TRUE ~ type
          )) %>% 
      filter_at(vars(starts_with(contains_text)), any_vars(!is.na(.))) %>%
      complete(participant_id, response_no = full_seq(response_no, period = 1)) %>% 
    select(-timing,-type)# Was having trouble getting filter to work with curly curly operator so used this hack https://stackoverflow.com/questions/54350264/dplyr-unquoting-does-not-work-with-filter-function
}

temp %>% 
  tidy_two_underscore(contains_text = "sad")

```
Fuck, this won't work when there are a different number of underscores across certain variables!! Wow this dataset is actually kind of impossible to clean.

Next step is to figure out where this procedure works vs. where it doesn't. I think this will work for variables that have 1-2 underscores but not 2-3 underscores across the various variables that need to be tidied

New note: The procedure seems to work on 2-3 underscore variables that don't have multiple variables with the same starting characters. For example, aware doesn't work this way because it has three versions where "aware" comes first (aware_mood, aware_felt_worse, aware_felt_better)

```{r}

## Extracting all two underscore variables

two_under <- temp %>% 
  names() %>% 
  enframe() %>% 
  filter(str_count(value, "_") == 2) %>% 
  select(value) %>% # Up to here is getting the 2 underscore variables only
  separate(value, into = c("first", "rest"), "_") %>% 
  distinct(first) %>% # Now getting the identifying part of each string, the first part before the first underscore
  filter(first != "time" & first != "aware" & first != "reminder" & first != "easy" & first != "notice") %>% # Not taking care of the timing variables here
  deframe() %>% 
  print()

## Mapping over those variables to create tidy versions of those variables

tidy_cols <- map(two_under, ~{
  temp %>% 
    tidy_two_underscore(contains_text = .x)
}) %>% 
  print()

```

Ok, what do I still have to figure out how to tidy?
- All the variables that start with "reminder" (3 versions orig/v2/347, two types day/night, five variables 1/2/3/4/5)
- All the variables that start with "aware" (2 versions, orig/v2, one type, three variables felt_better/felt_worse/mood)
- easy_use variables (2 versions, orig/v2, one type, one variable)
- five_times_per_day variables (2 versions, orig/v2, one type, one variable)
- notice_change variables (2 versions, orig/v2, one type, one variable)
- time_complete variables (2 versions, orig/v2, one type, one variable)

Probably need three separate solutions. One for reminder variables, one for aware variables, and one for remaining variables

```{r}

temp %>% 
  select(-contains("bad"), -contains("best"),-contains("control"), -contains("energy"),-contains("focus"),-contains("fun"),-contains("interest"),-contains("movement"),
         -contains("other"),-contains("sad"),-contains("thankyou"),-contains("worst")) %>% 
  skim()

```

For reminder variables, try some kind of regular expression where we combine variables that have "reminder_ANYTHING_1_ANYTHINGORNOTHING" for 1-5

```{r}

# Test outside function once

num <- 1

temp %>% 
  select(participant_id, response_no, matches(glue("reminder_.*_{num}+$")), matches(glue("reminder_.*_{num}_.*$"))) %>%
  pivot_longer(cols = c(matches(glue("reminder_.*_{num}+$")), matches(glue("reminder_.*_{num}_.*$"))),
               names_to = c(".value", "timing", "number", "type"),
               names_sep = "_") %>% 
  mutate(type = case_when(
    is.na(type) ~ "orig",
    TRUE ~ type
  )) %>% 
  filter_at(vars(starts_with("reminder")), any_vars(!is.na(.))) %>% 
  complete(participant_id, response_no = full_seq(response_no, period = 1)) %>% 
  rename("reminder_{num}" := reminder) %>% 
  select(-number)

## Create tidy function

tidy_reminder_vars <- function(.data, num){
  .data %>% 
  select(participant_id, response_no, matches(glue("reminder_.*_{num}+$")), matches(glue("reminder_.*_{num}_.*$"))) %>%
  pivot_longer(cols = c(matches(glue("reminder_.*_{num}+$")), matches(glue("reminder_.*_{num}_.*$"))),
               names_to = c(".value", "timing", "number", "type"),
               names_sep = "_") %>% 
  mutate(type = case_when(
    is.na(type) ~ "orig",
    TRUE ~ type
  )) %>% 
  filter_at(vars(starts_with("reminder")), any_vars(!is.na(.))) %>% 
  complete(participant_id, response_no = full_seq(response_no, period = 1)) %>% 
  rename("reminder_{num}" := reminder) %>% 
  select(-number,-timing,-type)
}

## Map over tidy function

tidy_reminder_cols <- map(1:5, ~{
  temp %>% 
    tidy_reminder_vars(num = .x)
})  %>% 
  reduce(left_join, by = c("participant_id","response_no")) %>% 
  print()



```

Tidy aware_felt_better

```{r}

tidied_aware_better <- temp %>% 
      select(participant_id, response_no, contains("aware_felt_better")) %>%
      pivot_longer(cols = contains("aware_felt_better"),
               names_to = c(".value", "timing", "type"),
               names_sep = "_") %>% 
      mutate(type = case_when(
            is.na(type) ~ "orig",
            TRUE ~ type
          )) %>% 
      filter_at(vars(starts_with("aware")), any_vars(!is.na(.))) %>%
      complete(participant_id, response_no = full_seq(response_no, period = 1)) %>% 
      select(-timing,-type) %>% 
      rename(aware_felt_better = aware) %>% 
      print() 

```


Tidy aware_felt_worse

```{r}

tidied_aware_worse <- temp %>% 
      select(participant_id, response_no, contains("aware_felt_worse")) %>%
      pivot_longer(cols = contains("aware_felt_worse"),
               names_to = c(".value", "timing", "type"),
               names_sep = "_") %>% 
      mutate(type = case_when(
            is.na(type) ~ "orig",
            TRUE ~ type
          )) %>% 
      filter_at(vars(starts_with("aware")), any_vars(!is.na(.))) %>%
      complete(participant_id, response_no = full_seq(response_no, period = 1)) %>% 
      select(-timing,-type) %>% 
      rename(aware_felt_worse = aware) %>% 
      print() 

```

Tidy aware_mood

```{r}

tidied_aware_mood <- temp %>% 
      select(participant_id, response_no, contains("aware_mood")) %>%
      pivot_longer(cols = contains("aware_mood"),
               names_to = c(".value", "timing", "type"),
               names_sep = "_") %>% 
      mutate(type = case_when(
            is.na(type) ~ "orig",
            TRUE ~ type
          )) %>% 
      filter_at(vars(starts_with("aware")), any_vars(!is.na(.))) %>%
      complete(participant_id, response_no = full_seq(response_no, period = 1)) %>% 
      select(-timing,-type) %>% 
      rename(aware_mood = aware) %>% 
      print() 

```

Tidy easy_use

```{r}

tidied_easy_use <- temp %>% 
      select(participant_id, response_no, contains("easy_use")) %>%
      pivot_longer(cols = contains("easy_use"),
               names_to = c(".value", "timing", "type"),
               names_sep = "_") %>% 
      mutate(type = case_when(
            is.na(type) ~ "orig",
            TRUE ~ type
          )) %>% 
      filter_at(vars(starts_with("easy")), any_vars(!is.na(.))) %>%
      complete(participant_id, response_no = full_seq(response_no, period = 1)) %>% 
      select(-timing,-type) %>% 
     rename(easy_use = easy) %>% 
      print() 

```

Tidy five_times_per_day

```{r}

tidied_five <- temp %>% 
      select(participant_id, response_no, contains("five_times_per_day")) %>%
      pivot_longer(cols = contains("five_times_per_day"),
               names_to = c(".value", "timing", "type", "day"),
               names_sep = "_") %>% 
      mutate(type = case_when(
            is.na(type) ~ "orig",
            TRUE ~ type
          )) %>% 
      filter_at(vars(starts_with("five")), any_vars(!is.na(.))) %>%
      complete(participant_id, response_no = full_seq(response_no, period = 1)) %>% 
      select(-timing,-type,-day) %>% 
      rename(five_times_per_day = five) %>% 
      print() 

```

Tidy notice_change

```{r}

tidied_notice_change <- temp %>% 
      select(participant_id, response_no, contains("notice_change")) %>%
      pivot_longer(cols = contains("notice_change"),
               names_to = c(".value", "timing"),
               names_sep = "_") %>% 
      filter_at(vars(starts_with("notice")), any_vars(!is.na(.))) %>%
      complete(participant_id, response_no = full_seq(response_no, period = 1)) %>% 
      select(-timing) %>% 
      rename(notice_change = notice) %>% 
      print() 

```

Tidy time_complete

```{r}

tidied_time_complete <- temp %>% 
      select(participant_id, response_no, contains("time_complete")) %>%
      pivot_longer(cols = contains("time_complete"),
               names_to = c(".value", "timing"),
               names_sep = "_") %>% 
      filter_at(vars(starts_with("time")), any_vars(!is.na(.))) %>%
      complete(participant_id, response_no = full_seq(response_no, period = 1)) %>% 
      select(-timing) %>% 
      rename(time_complete = time) %>% 
      print() 

```

Next steps: 
- Create reduced data frame of columns that didn't need tidying
- Join all the tidied columns to that data frame
- Be done!

Create reduced data frame with columns that didn't need tidying

```{r}

temp %>% 
  select(-contains("bad"), -contains("best"),-contains("control"), -contains("energy"),-contains("focus"),-contains("fun"),-contains("interest"),-contains("movement"),
         -contains("other"),-contains("sad"),-contains("thankyou"),-contains("worst"), -contains("reminder"), -contains("aware"),-contains("easy_use"),
         -contains("five_times_a_day"), -contains("five_times_per_day"), -contains("notice_change"), -contains("time_complete")) %>% 
  skim()

reduced_df <- temp %>% 
  select(-contains("bad"), -contains("best"),-contains("control"), -contains("energy"),-contains("focus"),-contains("fun"),-contains("interest"),-contains("movement"),
         -contains("other"),-contains("sad"),-contains("thankyou"),-contains("worst"), -contains("reminder"), -contains("aware"),-contains("easy_use"),
         -contains("five_times_a_day"), -contains("five_times_per_day"), -contains("notice_change"), -contains("time_complete")) %>% 
  print()

```

Join all tidied columns to this data frame by participant_id and response_no

```{r}

# First need to join all of tidied columns that are in a list together using reduce

tidy_cols_df <- tidy_cols %>% 
  reduce(left_join, by = c("participant_id", "response_no")) %>% 
  select(-contains("experience"))

# Joining all tidied columns with original data frame

reduced_df %>% 
  left_join(tidy_cols_df, by = c("participant_id", "response_no")) %>% 
  left_join(tidy_reminder_cols, by = c("participant_id", "response_no")) %>% 
  left_join(tidied_aware_better, by = c("participant_id", "response_no")) %>% 
  left_join(tidied_aware_worse, by = c("participant_id", "response_no")) %>% 
  left_join(tidied_aware_mood, by = c("participant_id", "response_no")) %>% 
  left_join(tidied_easy_use, by = c("participant_id", "response_no")) %>% 
  left_join(tidied_five, by = c("participant_id", "response_no")) %>% 
  left_join(tidied_notice_change, by = c("participant_id", "response_no")) %>% 
  left_join(tidied_time_complete, by = c("participant_id", "response_no")) %>% 
  skim()

tidy_lifepak_p1 <- reduced_df %>% 
  left_join(tidy_cols_df, by = c("participant_id", "response_no")) %>% 
  left_join(tidy_reminder_cols, by = c("participant_id", "response_no")) %>% 
  left_join(tidied_aware_better, by = c("participant_id", "response_no")) %>% 
  left_join(tidied_aware_worse, by = c("participant_id", "response_no")) %>% 
  left_join(tidied_aware_mood, by = c("participant_id", "response_no")) %>% 
  left_join(tidied_easy_use, by = c("participant_id", "response_no")) %>% 
  left_join(tidied_five, by = c("participant_id", "response_no")) %>% 
  left_join(tidied_notice_change, by = c("participant_id", "response_no")) %>% 
  left_join(tidied_time_complete, by = c("participant_id", "response_no")) %>% 
  mutate(lifepak_id = str_extract(participant_id, "-.*"),
         lifepak_id = str_remove(lifepak_id, "-")) %>% 
  relocate(participant_id, lifepak_id, everything()) %>% 
  print()

```

```{r read in qualtrics data}

wide_qualtrics <- read_csv("cleaned_qualtrics_ttt_phase_1.csv")

wide_qualtrics %>% 
  select(contains("id"))

```
```{r}

id_qualtrics <- wide_qualtrics %>% 
  select(yb_life_pak_id) %>% 
  arrange(yb_life_pak_id) %>% 
  print()

id_lifepak <- tidy_lifepak_p1 %>% 
  select(lifepak_id) %>% 
  distinct(lifepak_id) %>% 
  arrange(lifepak_id) %>% 
#  filter(lifepak_id != "034516" & lifepak_id != "092521") %>% 
  print()

!id_qualtrics$yb_life_pak_id %in% id_lifepak$lifepak_id

id_qualtrics[c(34,61,103:106),]

!id_lifepak$lifepak_id %in%id_qualtrics$yb_life_pak_id

id_lifepak[c(6, 12, 17, 27, 34, 36, 56, 67, 97, 106),]

# Going through IDs

# Function

filter_id <- function(.data, id) {
  .data %>% 
  select(yb_lsmh_id, yb_life_pak_id) %>% 
  filter(yb_lsmh_id == id)
}

lost_ids <- c("LSMH00097", "LSMH00306", "LSMH00457", "LSMH00617", "LSMH00681", "LSMH00483", "LSMH00416")

qualtrics_missing <- map_dfr(lost_ids, ~{
  wide_qualtrics %>% 
    filter_id(id = .x)
}) %>% 
  print()

# Trying to figure out if any of these potentially incorrect IDs are matching up with anything in the Lifepak data

qualtrics_missing %>% 
  filter(!is.na(yb_life_pak_id)) %>% 
  filter(yb_life_pak_id %in% id_lifepak$lifepak_id)

# Confirming no other ids have NA for lifepak id within the Qualtrics data

wide_qualtrics %>% 
  filter(is.na(yb_life_pak_id)) %>% 
  select(yb_lsmh_id)


```
```{r correcting ids in qualtrics}

id_corrected_qualtrics <- wide_qualtrics %>% 
  filter(yb_lsmh_id != "LSMH00062") %>% 
  mutate(yb_life_pak_id = case_when(
    yb_lsmh_id == "LSMH00097" ~ "092521",
    yb_lsmh_id == "LSMH00306" ~ "130294",
    yb_lsmh_id == "LSMH00457" ~ "292656",
    yb_lsmh_id == "LSMH00617" ~ "479327",
    yb_lsmh_id == "LSMH00681" ~ "510530",
    yb_lsmh_id == "LSMH00483" ~ "558692",
    yb_lsmh_id == "LSMH00416" ~ "946021",
    TRUE ~ yb_life_pak_id
  ))

```

```{r correcting ids in lifepak}

id_corrected_lifepak <- tidy_lifepak_p1 %>% 
  filter(lifepak_id != "234803" & lifepak_id != "878753" & lifepak_id != "297469")
```


```{r join qualtrics and lifepak data}

all_ttt_data <- left_join(id_corrected_lifepak, id_corrected_qualtrics, by = c("lifepak_id" = "yb_life_pak_id"))

write_csv(all_ttt_data, "cleaned_combined_qualtrics_lifepak_ttt_phase_1.csv")

```

```{r writing lifepak data}

write_csv(id_corrected_lifepak, "cleaned_lifepak_ttt_phase_1.csv")

```

```{r}

write_csv(id_corrected_qualtrics, "cleaned_qualtrics_ttt_phase_1.csv")

```

